Individual heterogeneity in the functional network topography of medial prefrontal

### 2019-08-30 Manuscript.Rmd
working sulcal relationship. needs polishing though

# update Summaries dfs
curvData <- lapply(files, function(file) {read.table(file, header = F)$V1[Summaries[[1]]$Vertex]})
for (i in seq(nSubj)) {
  Summaries[[i]]$Curvature <- curvData[[i]]
}

# select vmPFC like Lopez-Persem

>>>>

# select vmPFC like Lopez-Persem
# select bilateral parcels that cover the mask seen in fig. 4B in Lopez-Persem et al. 2019
# the parcels surrounding sulci ROS-S and SU-ROS are: a24, p32, s32, 10r
persemROI <- c("_25_", "_s32_", "_a24_", "_10v_", "_10r_", "_p32_")
primarySulci <- c("L_a24_ROI", "R_a24_ROI", "L_s32_ROI", "R_s32_ROI", "L_p32_ROI", "R_p32_ROI", "L_10r_ROI", "R_10r_ROI")

# update Summaries dfs, and reduce to vmPFC only
curvData <- lapply(files, function(file) {read.table(file, header = F)$V1[Summaries[[1]]$Vertex]})
for (i in seq(nSubj)) {
  Summaries[[i]]$Curvature <- curvData[[i]]
  Summaries[[i]]$SubjID <- subjList[[i]]
}

curvVmpfc <- lapply(Summaries, getCoords, Labels = persemROI)
curvVmpfc <- lapply(curvVmpfc, "[[", "Coords")

# compute per-subject correlations between Fiedler Vector and curvature
curvCors <- sapply(curvVmpfc, function(subj) {cor(subj$Curvature, subj$FiedlerVec)})

# mimic the binning and averaging they did
do.call(rbind, curvVmpfc) %>%
  mutate(Curvature = round(Curvature, digits = 1)) %>%
  filter(Curvature > -0.3,
         FiedlerVec > 0.01) %>%
  group_by(SubjID, Curvature) %>%
  summarise(mFV = mean(FiedlerVec)) %>%
  group_by(Curvature) %>%
  summarise(meanFV = mean(mFV),
            seFV = sd(mFV, na.rm = T) / sqrt(100)) %>%
  ggplot(aes(Curvature, meanFV)) +
    geom_point(show.legend = F, size = 1.5) +
    geom_errorbar(aes(Curvature, ymin = meanFV - seFV, ymax = meanFV + seFV), width = 0.01, size = 1) +
    theme_classic()
```
